Fusing Filters with Integer Linear Programming

### 2014-05-15 2014betterfusionforfilters/section/03-SizeInference.tex
Clarification of combinator vs name
in binding of combinator application

Looking back at the @normalize2@ example, the iteration size of @gts@ and @sum1@ are both $k_{xs}$.
%The iteration size of @sum2@ is $k_{gts}$, and @gts@ is a transducer from $k_{xs}$ to $k_{gts}$. 
%\gabi{gts is no combinator, so can't be a transducer
The iteration size of @sum2@ is $k_{gts}$, and the filter combinator which produces @gts@ is a transducer from $k_{xs}$ to $k_{gts}$. 
Even though $k_{gts}$ is not equal to $k_{xs}$, the three nodes @gts@, @sum1@ and @sum2@ can all be fused together.
The two nodes @sum2@ and @gts@ can be fused together, since the output size of @gts@ is the iteration size of @sum2@.
Similarly, @sum1@ and @gts@ can be fused together, as they have the same iteration size.
\begin{code}
 normalize2 xs
  = let sum1 = fold   (+)  0   xs
        gts  = filter (> 0)    xs
        sum2 = fold   (+)  0   gts
        ...
\end{code}

% \ben{Do other systems use the concept of transducers?} \TODO{Explain that a transducer of filter is the filter's parent. so $trans(trans(n)) \not= n$}
% No,
We now define a function $trans$, to find the parent transducer of a given combinator.
The parent transducer $trans(bs, n)$ of a combinator $n$ has the same output size as $n$'s iteration size, but the two have different iteration sizes.

>>>>

Looking back at the @normalize2@ example, the iteration sizes of the combinators of @gts@ and @sum1@ are both $k_{xs}$.
%The iteration size of @sum2@ is $k_{gts}$, and @gts@ is a transducer from $k_{xs}$ to $k_{gts}$. 
%\gabi{gts is no combinator, so can't be a transducer
The iteration size of @sum2@ is $k_{gts}$, and the filter combinator which produces @gts@ is a transducer from $k_{xs}$ to $k_{gts}$. 
Even though $k_{gts}$ is not equal to $k_{xs}$, the three nodes @gts@, @sum1@ and @sum2@ can all be fused together.
The two nodes @sum2@ and @gts@ can be fused together, since the output size of @gts@ is the iteration size of @sum2@.
Similarly, @sum1@ and @gts@ can be fused together, as they have the same iteration size.
\begin{code}
 normalize2 xs
  = let sum1 = fold   (+)  0   xs
        gts  = filter (> 0)    xs
        sum2 = fold   (+)  0   gts
        ...
\end{code}

% \ben{Do other systems use the concept of transducers?} \TODO{Explain that a transducer of filter is the filter's parent. so $trans(trans(n)) \not= n$}
% No,
We now define a function $trans$, to find the parent transducer a combinator application. Since each name is bound to at most one combinator, we abuse terminology here slightly and write ``combinator $n$'' when refering to the combinator occuring in the binding of the name $n$.
The parent transducer $trans(bs, n)$ of a combinator $n$ has the same output size as $n$'s iteration size, but the two have different iteration sizes.
